A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-11 4_method.tex
discretization figure

In order to generate the VQ, we start by generating a normal Voronoi Diagram and remove all segments which lie outside of the boundary shape.
We then introduce bones such that each node in the VQ is directly connected to the outline via a single bone:
each node in the VQ is connected to the closest points on the boundary (its \emph{support}).
As such the VQ divides the polygon in quads consisting of 1 outline segment and 3 bones, one of which is not directly connected to the outline.
For concave verts the quad is missing the outline segments and so it regresses into a triangle;
likewise for convex sections it may happen that the inner bone is missing from the quad so that it forms a triangle.
\todo{TODO: make pics}

We then also discretize parabolic bones and bones generated by two concave outline vertices into approximately equidistant segments.
That way we can approximate the feature radius $R$ in between two nodes $v_0$ and $v_1$ in the VQ by interpolating linearly between $R(v_0)$ and $R(v_1)$.
Furthermore, we can linearly interpolate the distance field of a quad $p_0v_0v_1p_1$ (where $p_0$ and $p_1$ lie on the outline shape):
For a point $a \in p_0v_0$ and a point $b \in p_1v_1$ for which $R(a) = R(b)$ we have that all points in the line segment $ab$ have the same feature radius $R$.

>>>>

In order to generate the VQ, we start by generating a normal Voronoi Diagram and remove all segments which lie outside of the boundary shape.
We then introduce bones such that each node in the VQ is directly connected to the outline via a single bone:
each node in the VQ is connected to the closest points on the boundary (its \emph{support}).
As such the VQ divides the polygon in quads consisting of 1 outline segment and 3 bones, one of which is not directly connected to the outline.
However some of these quads are triangles, as can be seen in \cref{discretization}.

We then also discretize parabolic bones and bones generated by two concave outline vertices into approximately equidistant segments.
See \cref{discretization}.
That way we can approximate the feature radius $R$ in between two nodes $v_0$ and $v_1$ in the VQ by interpolating linearly between $R(v_0)$ and $R(v_1)$.
Furthermore, we can linearly interpolate the distance field of a quad $p_0v_0v_1p_1$ (where $p_0$ and $p_1$ lie on the outline shape):
For a point $a \in p_0v_0$ and a point $b \in p_1v_1$ for which $R(a) = R(b)$ we have that all points in the line segment $ab$ have the same feature radius $R$.

\begin{figure}
\centering
\includegraphics[width=.5\columnwidth]{sources/method/parabola_dip.pdf}
\caption{
Construction of a VQ:
the MAT in red,
the bones added by VD in purple,
the bones added by VQ in orange,
the bones added by discretization in dashed lines.
The 3 types of quad are highlighted.
}
\label{discretization}
\end{figure}
